Exploring dimensions of biodiversity in Japanese ferns

### 2021-05-27 ms/manuscript.Rmd
Move ms rendering functions to separate file

```{r setup, include=FALSE}
library(officedown)
library(officer)
library(flextable)
library(kableExtra)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, results = "hide", cache = FALSE)

@@

```{r macros}
# Define formattting for some common custom words that may vary in style between journals
ie <- "*ie*"
eg <- "*eg*"
# R packages
pack <- function(x) {glue::glue("'{x}'")}
# R functions
func <- function(x) {glue::glue("'{x}'")}
# Pagebreak for MS Word (doc) only
pagebreak_doc <- function() {ifelse(params$doc_type == "doc", run_pagebreak(), return(""))}
# Pagebreak for pdf only
pagebreak_pdf <- function() {ifelse(params$doc_type == "pdf", return("\\clearpage"), return(""))}
# Pagebreak for both
pagebreak <- function() {
  if (params$doc_type == "doc") {
    run_pagebreak()
  } else if (params$doc_type == "pdf") {
    return("\\clearpage")
  } else {
    stop("doc_type parameter must be 'doc' or 'pdf'")
  }
}
```

```{r load-data}
tar_load(c(
  "occ_point_data_ferns",
  "occ_point_data_ferns_unfiltered",
  "biodiv_ferns_spatial",
  "k_taxonomy",
  "k_phylogeny",
  "signif_cells_protected_area",
  "protected_areas",
  "japan_shp",
  "phy_sig_results",
  "binary_sig_results",
  "traits_summary",
  "fern_traits",
  "japan_pterido_tree",
  "japan_fern_tree",
  "ppgi",
  "occ_point_data_ferns",
  "comm_ferns_full",
  "comm_ferns",
  "japan_points_raw",
  # "plastome_calibration_dates",
  # FIXME: remove until phylo analysis is working "plastome_tree",
  "green_list"
))
```

>>>>

```{r setup, include = FALSE}
# Load libraries used for rendering Rmds
library(officedown)
library(officer)
library(flextable)
library(kableExtra)

# Set knitr options
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, results = "hide", cache = FALSE)

# Load functions only used when rendering Rmds
source(here::here("R/ms_functions.R"), local = TRUE)

@@

```{r load-data}
# Load objects from targets workflow
tar_load(c(
  "occ_point_data_ferns",
  "occ_point_data_ferns_unfiltered",
  "biodiv_ferns_spatial",
  "k_taxonomy",
  "k_phylogeny",
  "signif_cells_protected_area",
  "protected_areas",
  "japan_shp",
  "phy_sig_results",
  "binary_sig_results",
  "traits_summary",
  "fern_traits",
  "japan_pterido_tree",
  "japan_fern_tree",
  "ppgi",
  "occ_point_data_ferns",
  "comm_ferns_full",
  "comm_ferns",
  "japan_points_raw",
  # "plastome_calibration_dates",
  # FIXME: remove until phylo analysis is working "plastome_tree",
  "green_list"
))
```
